Viz Creation

### 2021-05-06 code/Viz Creation.Rmd
imgs

```{r}
pew %>% drop_na(CONCERNCO_W49) %>% filter(CONCERNCO_W49 != "Refused") %>% ggplot(aes(x = CONCERNCO_W49, fill = CONCERNCO_W49)) +
  geom_bar(color = 'black') +
  facet_wrap(. ~groupKnow, scales = "free_y") +
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_blank()) +
  labs (
    title = "Concern Of Company Tracking Faceted on Tech Literacy",
    # subtitle = "Optional",
    fill = "How Concerned Are You\nAbout Companies Tracking You?",
    x = "Tech Literacy Level",
    caption = "Series 2 Picture 4\nNo Literacy = 0/6\nSome Literacy = [1/6, 4/6]\nHigh Literacy = [5/6, 6/6]"
  )
```
This is interesting because the concern drops as people gain a higer litercay

```{r}
levels(pew$PROFILE4_W49)
pew %>% drop_na(PROFILE4_W49) %>% filter(PROFILE4_W49 != "Refused") %>% ggplot(aes(x = PROFILE4_W49, fill = PROFILE4_W49)) +
  geom_bar(color = 'black') +
  facet_wrap(. ~groupKnow, scales = "free_y") +
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_blank()) +
  labs (
    title = "Understanding of Targeted Ad Data Faceted on Tech Literacy",
    # subtitle = "Optional",
    fill = "Do You Understand What Data\nIs Used To Create Targeted Ads?",
    x = "Tech Literacy Level",
    caption = "Series 2 Picture 4\nNo Literacy = 0/6\nSome Literacy = [1/6, 4/6]\nHigh Literacy = [5/6, 6/6]"
  )
```
The interesting takeaway here is that regardless of tech litercay people don't understand what data is used to target them. This is interesting because I HAVE ANOTHER CORRELATION TO SHOW THAT LITERACY AND TECH WORRY are hand in hand

@@

## Rename Cols
df_f3  <- df_f3  %>% 
  rename("Advertisers' Use Of Facial Recognition" = FACE3a_W49,
          "Tech Companies' Use Of Facial Recognition" = FACE3b_W49,
          "Law Enforcement's Use Of Facial Recognition" = FACE3c_W49)
df_f3  <- as.data.frame(df_f3)
df_f3 <- droplevels(df_f3) #remove unused levels

@@

## Generate Title
title2 <- "Trust In Responsible Use Of Facial Recognition Tech\nFaceted on Tech Litercay"
```

@@

## Center with percents
plot(likert(df_f3.reverse[,c(1:3)], grouping = df_f3.reverse[,4]), legend.position="right", centered = TRUE, plot.percents=FALSE, plot.percent.low=TRUE, plot.percent.high=TRUE, plot.percent.neutral=TRUE, center = 2.5) + 
  scale_fill_manual(values = brewer.pal(n=4,"RdBu"), breaks = c("Not at all", "Not too much", "Somewhat", "A great deal")) + #order and color the likert boxes
  ggtitle(title2) +
  guides(fill = guide_legend(title="Responses", reverse = TRUE)) #to reverse the order in the legend
ggsave(file = "../imgs/FACE3_center_percents.png")

## Center No Percents 
plot(likert(df_f3.reverse[,c(1:3)], grouping = df_f3.reverse[,4]), legend.position="right", centered = TRUE, plot.percents=FALSE, plot.percent.low=FALSE, plot.percent.high=FALSE, plot.percent.neutral=FALSE, center = 2.5) + 
  scale_fill_manual(values = brewer.pal(n=4,"RdBu"), breaks = c("Not at all", "Not too much", "Somewhat", "A great deal")) + #order and color the likert boxes
  ggtitle(title2) +
  guides(fill = guide_legend(title="Responses", reverse = TRUE)) #to reverse the order in the legend
ggsave(file = "../imgs/FACE3_center.png")

@@

```{r}
plot(likert(df_f4.reverse[,c(1:4)], grouping = df_f4.reverse[,5]), legend.position="right", plot.percents=FALSE, plot.percent.low=FALSE, plot.percent.high=FALSE, plot.percent.neutral=FALSE, center = 2.5) +
  scale_fill_manual(values = brewer.pal(n=4,"RdBu"), breaks = c("NA", "Not sure", "Unacceptable", "Acceptable")) + #order and color the likert boxes
  # scale_fill_manual(values = brewer.pal(n=4,"RdBu")) +
  ggtitle(title1) +
  guides(fill = guide_legend(title="Responses", reverse = TRUE)) #to reverse the order in the legend

>>>>

```{r}
pew %>% drop_na(CONCERNCO_W49) %>% filter(CONCERNCO_W49 != "Refused") %>% ggplot(aes(x = CONCERNCO_W49, fill = CONCERNCO_W49)) +
  geom_bar(color = 'black') +
  facet_wrap(. ~groupKnow, scales = "free_y") +
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_blank()) +
  labs (
    title = "Concern Of Company Tracking Faceted on Tech Literacy",
    # subtitle = "Optional",
    fill = "How Concerned Are You\nAbout Companies Tracking You?",
    x = "Tech Literacy Level",
    caption = "Series 2 Picture 4\nNo Literacy = 0/6\nSome Literacy = [1/6, 4/6]\nHigh Literacy = [5/6, 6/6]"
  )
ggsave(file = "../imgs/CONCERNCO.png")
```
This is interesting because the concern drops as people gain a higer litercay

```{r}
levels(pew$PROFILE4_W49)
pew %>% drop_na(PROFILE4_W49) %>% filter(PROFILE4_W49 != "Refused") %>% ggplot(aes(x = PROFILE4_W49, fill = PROFILE4_W49)) +
  geom_bar(color = 'black') +
  facet_wrap(. ~groupKnow, scales = "free_y") +
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_blank()) +
  labs (
    title = "Understanding of Targeted Ad Data Faceted on Tech Literacy",
    # subtitle = "Optional",
    fill = "Do You Understand What Data\nIs Used To Create Targeted Ads?",
    x = "Tech Literacy Level",
    caption = "Series 2 Picture 4\nNo Literacy = 0/6\nSome Literacy = [1/6, 4/6]\nHigh Literacy = [5/6, 6/6]"
  )
ggsave(file = "../imgs/PROFILE4.png")
```
The interesting takeaway here is that regardless of tech litercay people don't understand what data is used to target them. This is interesting because I HAVE ANOTHER CORRELATION TO SHOW THAT LITERACY AND TECH WORRY are hand in hand

@@

## Rename Cols
df_f3  <- df_f3  %>% 
  rename("Advertisers' Use Of Facial Recognition" = FACE3a_W49,
          "Tech Companies' Use Of Facial Recognition" = FACE3b_W49,
          "Law Enforcement's Use Of Facial Recognition" = FACE3c_W49)
df_f3  <- as.data.frame(df_f3)
df_f3 <- droplevels(df_f3) #remove unused levels 
df_f3 <- df_f3[, c(1,3,2,4)] #change order of cols for facets to come in nice order

@@

## Generate Title
title2 <- "Trust In Responsible Use Of Facial Recognition Tech\nFaceted on Tech Literacy"
```

@@

## Center with percents
plot(likert(df_f3.reverse[,c(1:3)], grouping = df_f3.reverse[,4]), legend.position="right", centered = TRUE, plot.percents=FALSE, plot.percent.low=TRUE, plot.percent.high=TRUE, plot.percent.neutral=FALSE, center = 2.5, text.color = 'purple') + 
  scale_fill_manual(values = brewer.pal(n=4,"RdBu"), breaks = c("Not at all", "Not too much", "Somewhat", "A great deal")) + #order and color the likert boxes
  ggtitle(title2) +
  guides(fill = guide_legend(title="Responses", reverse = TRUE)) #to reverse the order in the legend
ggsave(file = "../imgs/FACE3_center_percents.png")

## Center No Percents 
plot(likert(df_f3.reverse2[,c(1:3)], grouping = df_f3.reverse[,4]), legend.position="right", centered = TRUE, plot.percents=TRUE, plot.percent.low=FALSE, plot.percent.high=FALSE, plot.percent.neutral=FALSE, center = 2.5) + 
  scale_fill_manual(values = brewer.pal(n=4,"RdBu"), breaks = c("Not at all", "Not too much", "Somewhat", "A great deal")) + #order and color the likert boxes
  ggtitle(title2) +
  guides(fill = guide_legend(title="Responses", reverse = TRUE)) #to reverse the order in the legend
ggsave(file = "../imgs/FACE3_center.png")

@@

```{r}
plot(likert(df_f4.reverse[,c(1:4)], grouping = df_f4.reverse[,5]), legend.position="right", plot.percents=FALSE, plot.percent.low=FALSE, plot.percent.high=FALSE, plot.percent.neutral=FALSE, center = 2.5) +
  scale_fill_manual(values = brewer.pal(n=4,"RdBu"), breaks = c("NA", "Not sure", "Unacceptable", "Acceptable")) + #order and color the likert boxes
  # scale_fill_manual(values = brewer.pal(n=4,"RdBu")) +
  ggtitle(title1) +
  guides(fill = guide_legend(title="Responses", reverse = TRUE)) #to reverse the order in the legend
ggsave(file = "../imgs/FACE4.png")
